Plots for Latent Hawkes Paper

### 2020-12-14 output_scripts/Slide_Plots.Rmd
add Rmd for slide plots

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "paper_figure/",
                      dev = 'png', fig.height = 4.5, fig.width = 7,
                      warning = FALSE)

@@

```{r load rankings,echo=FALSE,include=FALSE,results='hide',cache=TRUE}
full_data <- readRDS("../data/mice.RData")
# A=c9, B=c10, C=c12, D=c15, E=c16, F=c17, G=c18, H=c37, I=c38. J=c45

@@

```{r define_functions}
model1_fn <- list(alpha.fun = function(x,y,eta1,eta2,eta3){return(eta1*x*y*exp(-eta2*abs(x-y))/(1 +
                                                        exp(-eta3*(x-y))))})

@@

```{r creat colour df}
col_df <- tibble(method = c("I&SI", "AggRank", "DSNL", "Glicko", "I-MMHP",
            "C-HP", "C-DCHP", "True", "C-MMHP"),
            cols = viridis(9))

@@

# Figure 5b: Simulation Spearman Rank
```{r fig-5b-spearman-sim, fig.height=7}
sim_files <- list.files(here("output", "sims_m3_update"), 
                        pattern = "rank_sim")

@@

sim_data %>%
  rename(Method = name, corr = value) %>%
  ggplot(aes(Method,corr)) + 
  geom_boxplot(aes(fill = Method), alpha = 0.7) +
  scale_fill_manual(values = plot_cols) +
  labs(y = "Rank Correlation") + theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_blank(),
        axis.ticks.x = element_blank(),
        legend.position="right") + ggtitle("(b)")
```

@@

```{r fig-6a-rank-vs-isi}
### Rank Comparison for Single Cohort ####
# current_cohort <- 5

@@

p1 <- ggplot(plot_latent_df, 
             aes(x = Mice, y = force, fill = Method)) +
  geom_boxplot(alpha=0.7) +
  scale_fill_manual(values = plot_cols)+
  #scale_fill_manual(values = c("gray", "steelblue", "goldenrod2" , "firebrick2")) +
  ggtitle("(a)") +
  theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_text(size = 10),
        legend.position="none") +
  facet_grid(cols=vars(Method)) +
  xlab("Mice (ranked by I&SI method)") +
  ylab("Latent rank")
p1
#dev.off()

@@

```{r fig-6b-overall-rank-correlation}
load("../output/weighted_rank_data.RData")
#png(paste(plot_path,"real_rank_all_cohort.png",sep=""),width=600,height=300)
no_method <- 4
plot_cor_df <- data.frame(Method=rep(c(1:no_method),each=10),
                          cor=as.vector(spearman_df))
plot_cor_df$Method <- factor(plot_cor_df$Method,
                             labels = c("Agg-rank","C-HP","C-DCHP","C-MMHP"))
p2 <- ggplot(plot_cor_df, aes(x="", y = cor, fill = Method)) +
        geom_boxplot(alpha=0.7, width=0.5) +
        scale_fill_manual(values = plot_cols) + 
        ggtitle("(b)") +
        ylim(0,1) +
        theme_bw() +
        theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
              text = element_text(size = 20),
              axis.text.y =element_text(size = 11),
              legend.position="none",
              axis.title.x=element_blank()) +
        facet_grid(cols=vars(Method)) +
        ylab("Spearman rank correlation")
p2

@@

```{r fig-7-prMatrix-Cohort3, fig.width=7, fig.height=7}
current_cohort <- 3
## 2 and 8 maybe look better
## 3 probably looks the best

@@

matrix_lst_plot <- list(
                        indep_pr[rev(expert_rank_10[[current_cohort]]),
                                                                   expert_rank_10[[current_cohort]]],
                        m1_pr[rev(expert_rank_10[[current_cohort]]),
                                                                 expert_rank_10[[current_cohort]]],
                        m2_pr[rev(expert_rank_10[[current_cohort]]),
                                                                 expert_rank_10[[current_cohort]]],
                        m3_pr[rev(expert_rank_10[[current_cohort]]),
                                                                 expert_rank_10[[current_cohort]]]) 
#cat("Cohort ",current_cohort,"\n",sep="")
myMultiMatrixPlot(X=matrix_lst_plot,no_matrix=4,n_row=2,
                  xLabels=expert_rank_10[[current_cohort]],
                  yLabels=rev(expert_rank_10[[current_cohort]]),
                  min=-80,max=80,axis_cex=2,title_cex = 1.8,
                  colorPalette="RdBu",if.emp=FALSE,
                  #legend.mar=c(0.5,.5,0.5,0.5),
                  title_lst=list("I-MMHP","C-HP","C-DCHP","C-MMHP"), 
                  #title_lst = list("I-MMHP"),
                  col_axis=c(-80,-40,0,40,80), fake_matrix=FALSE,
                  matrix.mar=c(2.5,2.5,2.5,1)
                  )
# mtext(text="(a)",side=3,line=0.5,outer=TRUE,cex=2.5,font=2)

@@

p3 <- temp_plot_df %>%
  rowwise() %>%
  #mutate(norm = min(norm,60)) %>%
  # rename(Method = method) %>%
  ggplot( aes(x = method, y = norm, fill = method)) +
  geom_boxplot(alpha=0.7) +
  scale_fill_manual(values = plot_cols_pred) +
  ggtitle("(a)") +
  theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_blank(),
        axis.ticks.x = element_blank(),
        legend.position="right") +
  facet_grid(cols=vars(day)) +
  xlab("Prediction horizon (day)") + 
  ylab("Frobenius norm of error") +
  ylim(0, 100) + # aren't infinite but >150 and <200
  NULL
p3 + labs(fill = "Method")
```

@@

```{r fig-7a-pred-all-cohorts-box}
load("../output/plot_N_predict.RData")

@@

all_cohort_box %>% 
  ggplot(aes(x=method,y=norm, fill = method)) +
  # facet_grid(cols = vars(day)) +
  geom_boxplot(alpha=0.7) +
  scale_fill_manual(values = plot_cols_pred) +
  ggtitle("(a)") +
  theme_bw() +
  theme(plot.title = element_text(size = 22,
                                  hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_blank(),
        axis.ticks.x = element_blank(),
        legend.position="right") +
  facet_grid(cols=vars(day)) +
  # guides(color=guide_legend(title="Method")) +
  xlab("Prediction horizon (day)") + 
  ylab("Frobenius norm of error") +
  labs(fill = "Method") +
  # ylim(0, 80) +
  NULL

@@

```{r fig-7b-pred-rank-spearman-all-cohorts}
load("../output/plot_rank_predict.RData")

@@

p7 <- ggplot(all_cohort_rank_df,
       aes(x=method, y=spearman, fill=method)) + 
  # geom_line(size=1.2, alpha=0.8, position=position_dodge(0.2)) +
  geom_boxplot(alpha = 0.7) +
  scale_fill_manual(values = plot_cols_pred) +
  ggtitle("(b)") +
  theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_blank(),
        axis.ticks.x = element_blank(), 
        legend.position="right") +
  facet_grid(cols = vars(day)) +
  xlab("Prediction horizon (day)") + 
  ylab("Spearman rank corr.") + 
  # coord_cartesian(ylim=c(0,1)) + 
  labs(fill = "Method")

@@

```{r construct data for plot, results='hide',message=FALSE,cache=TRUE}
library(PlayerRatings)

@@

```{r fig-10a-glicko-rating}
par(mar=c(3,5,3,1))
testing_end <- testing_end - 1
plot(1, type="n", xlab="", ylab="Glicko ranking", xlim=c(0,dim(gl$history)[2]),
     ylim=c(min(gl$history[,,1]),max(gl$history[,,1])),
     cex.axis=2, cex.lab=2)
for(m in c(1:mice_number)){
  #history
  lines(gl$history[m,1:training_end,1],
        cex=0.6, col=col_vec[m],lwd=history_width,lty=ltypes_vec[m])
  lines(c(rep(NA,training_end), gl$history[m,(training_end+1):testing_end,1]),
        cex=0.6, col=shade_vec[m],lwd=history_width,lty=ltypes_vec[m])

@@

# annotate the days
for(d in c(19:21)){
  abline(v = nrow(df[df$day<=(d-1),]),lty=2,lwd=0.4)
  text(x=nrow(df[df$day<=(d-1),]),y=2600,d)
}
mtext(text="(a)", side=3, line=-2.3, outer=TRUE, cex=2.8, at=0.5, font=2)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "slide_figure/",
                      dev = 'png', fig.height = 4.5, fig.width = 7,
                      warning = FALSE, eval = FALSE, include = FALSE)

@@

```{r load rankings,echo=FALSE,eval=TRUE,results='hide',cache=TRUE}
full_data <- readRDS("../data/mice.RData")
# A=c9, B=c10, C=c12, D=c15, E=c16, F=c17, G=c18, H=c37, I=c38. J=c45

@@

```{r define_functions,eval=TRUE}
model1_fn <- list(alpha.fun = function(x,y,eta1,eta2,eta3){return(eta1*x*y*exp(-eta2*abs(x-y))/(1 +
                                                        exp(-eta3*(x-y))))})

@@

```{r creat colour df,eval=TRUE}
col_df <- tibble(method = c("I&SI", "AggRank", "DSNL", "Glicko", "I-MMHP",
            "C-HP", "C-DCHP", "True", "C-MMHP"),
            cols = viridis(9))

@@

# Figure 5b: Simulation Spearman Rank
```{r fig-5b-spearman-sim, fig.height=3, fig.width=6, include=TRUE,eval=TRUE}
sim_files <- list.files(here("output", "sims_m3_update"), 
                        pattern = "rank_sim")

@@

sim_data %>%
  rename(Method = name, corr = value) %>%
  ggplot(aes(Method,corr)) + 
  geom_boxplot(aes(fill = Method), alpha = 0.7) +
  scale_fill_manual(values = plot_cols) +
  labs(y = "Rank Correlation") + theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_blank(),
        axis.ticks.x = element_blank(),
        legend.position="right") #+ ggtitle("(b)")
```

@@

```{r fig-6a-rank-vs-isi, include=TRUE, eval=TRUE}
### Rank Comparison for Single Cohort ####
# current_cohort <- 5

@@

p1 <- ggplot(plot_latent_df, 
             aes(x = Mice, y = force, fill = Method)) +
  geom_boxplot(alpha=0.7) +
  scale_fill_manual(values = plot_cols) +
  # ggtitle("(a)") +
  theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_text(size = 10),
        legend.position="none") +
  facet_grid(cols=vars(Method)) +
  xlab("Mice (ranked by I&SI method)") +
  ylab("Latent rank")
p1
#dev.off()

@@

```{r fig-6b-overall-rank-correlation, include=TRUE, eval=TRUE}
load("../output/weighted_rank_data.RData")
#png(paste(plot_path,"real_rank_all_cohort.png",sep=""),width=600,height=300)
no_method <- 4
plot_cor_df <- data.frame(Method=rep(c(1:no_method),each=10),
                          cor=as.vector(spearman_df))
plot_cor_df$Method <- factor(plot_cor_df$Method,
                             labels = c("Agg-rank","C-HP","C-DCHP","C-MMHP"))
p2 <- ggplot(plot_cor_df, aes(x="", y = cor, fill = Method)) +
        geom_boxplot(alpha=0.7, width=0.5) +
        scale_fill_manual(values = plot_cols) + 
        # ggtitle("(b)") +
        ylim(0,1) +
        theme_bw() +
        theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
              text = element_text(size = 20),
              axis.text.y =element_text(size = 11),
              legend.position="none",
              axis.title.x=element_blank()) +
        facet_grid(cols=vars(Method)) +
        ylab("Spearman rank correlation")
p2

@@

```{r fig-7-prMatrix-Cohort3, fig.width=7, fig.height=3, eval=TRUE, include=TRUE}
current_cohort <- 3
## 2 and 8 maybe look better
## 3 probably looks the best

@@

matrix_lst_plot <- list(
                        # indep_pr[rev(expert_rank_10[[current_cohort]]),
                        #                                            expert_rank_10[[current_cohort]]],
                        m1_pr[rev(expert_rank_10[[current_cohort]]),
                                                                 expert_rank_10[[current_cohort]]],
                        m2_pr[rev(expert_rank_10[[current_cohort]]),
                                                                 expert_rank_10[[current_cohort]]],
                        m3_pr[rev(expert_rank_10[[current_cohort]]),
                                                                 expert_rank_10[[current_cohort]]]) 
#cat("Cohort ",current_cohort,"\n",sep="")
myMultiMatrixPlot(X=matrix_lst_plot,no_matrix = 3,n_row = 1,
                  xLabels = expert_rank_10[[current_cohort]],
                  yLabels = rev(expert_rank_10[[current_cohort]]),
                  min = -80,max = 80,axis_cex = 2,
                  title_cex = 1.8,
                  colorPalette = "RdBu",if.emp = FALSE,
                  #legend.mar=c(0.5,.5,0.5,0.5),
                  title_lst = list("C-HP","C-DCHP","C-MMHP"), 
                  #title_lst = list("I-MMHP"),
                  col_axis = c(-80,-40,0,40,80), fake_matrix=FALSE,
                  matrix.mar = c(2.5,2.5,2.5,1)
                  )
# mtext(text="(a)",side=3,line=0.5,outer=TRUE,cex=2.5,font=2)

@@

p3 <- temp_plot_df %>%
  rowwise() %>%
  #mutate(norm = min(norm,60)) %>%
  # rename(Method = method) %>%
  ggplot( aes(x = method, y = norm, fill = method)) +
  geom_boxplot(alpha=0.7) +
  scale_fill_manual(values = plot_cols_pred) +
  # ggtitle("(a)") +
  theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_blank(),
        axis.ticks.x = element_blank(),
        legend.position="right") +
  facet_grid(cols=vars(day)) +
  xlab("Prediction horizon (day)") + 
  ylab("Frobenius norm of error") +
  ylim(0, 100) + # aren't infinite but >150 and <200
  NULL
p3 + labs(fill = "Method")
```

@@

```{r fig-7a-pred-all-cohorts-box, include=TRUE, eval=TRUE, fig.width=7,fig.height=3}
load("../output/plot_N_predict.RData")

@@

all_cohort_box %>% 
  ggplot(aes(x=method,y=norm, fill = method)) +
  # facet_grid(cols = vars(day)) +
  geom_boxplot(alpha=0.7) +
  scale_fill_manual(values = plot_cols_pred) +
  # ggtitle("(a)") +
  theme_bw() +
  theme(plot.title = element_text(size = 22,
                                  hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_blank(),
        axis.ticks.x = element_blank(),
        legend.position="right") +
  facet_grid(cols=vars(day)) +
  # guides(color=guide_legend(title="Method")) +
  xlab("Prediction horizon (day)") + 
  ylab("Frob. norm of error") +
  labs(fill = "Method") +
  # ylim(0, 80) +
  NULL

@@

```{r fig-7b-pred-rank-spearman-all-cohorts, include=TRUE, eval=TRUE, fig.width=7,fig.height=3}
load("../output/plot_rank_predict.RData")

@@

p7 <- ggplot(all_cohort_rank_df,
       aes(x=method, y=spearman, fill=method)) + 
  # geom_line(size=1.2, alpha=0.8, position=position_dodge(0.2)) +
  geom_boxplot(alpha = 0.7) +
  scale_fill_manual(values = plot_cols_pred) +
  # ggtitle("(b)") +
  theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_blank(),
        axis.ticks.x = element_blank(), 
        legend.position="right") +
  facet_grid(cols = vars(day)) +
  xlab("Prediction horizon (day)") + 
  ylab("Spearman rank corr.") + 
  # coord_cartesian(ylim=c(0,1)) + 
  labs(fill = "Method")

@@

```{r construct data for plot, results='hide',message=FALSE,cache=TRUE,eval=TRUE}
library(PlayerRatings)

@@

```{r fig-10a-glicko-rating,include=TRUE,eval=TRUE}
par(mar=c(3,5,3,1))
testing_end <- testing_end - 1
plot(1, type="n", xlab="", ylab="Glicko ranking", xlim=c(0,dim(gl$history)[2]),
     ylim=c(min(gl$history[,,1]),max(gl$history[,,1])),
     cex.axis=2, cex.lab=2)
for(m in c(1:mice_number)){
  #history
  lines(gl$history[m,1:training_end,1],
        cex=0.6, col=col_vec[m],lwd=history_width,lty=ltypes_vec[m])
  lines(c(rep(NA,training_end), gl$history[m,(training_end+1):testing_end,1]),
        cex=0.6, col=shade_vec[m],lwd=history_width,lty=ltypes_vec[m])

@@

# annotate the days
for(d in c(19:21)){
  abline(v = nrow(df[df$day<=(d-1),]),lty=2,lwd=0.4)
  text(x=nrow(df[df$day<=(d-1),]),y=2600,d)
}
# mtext(text="(a)", side=3, line=-2.3, outer=TRUE, cex=2.8, at=0.5, font=2)
```
